R Notebook

### 2021-04-19 FEM_R/model_analysis_core.Rmd
Many changes to get core scenarios working. Added ELSA_core_scen.csv file for running the core scenarios
Lots of small changes, committing altogether as would take forever to do piece by piece

# FEM 2014 summary
#FEM <- read_dta('ELSA_Baseline/ELSA_Baseline_summary.dta')
FEM <- read_dta('ELSA_AgeUK_valid/ELSA_AgeUK_valid_summary.dta')

@@

# Collect the age suffixes into a vector
keep_vars <- c(m_ages, f_ages)
# Now set up the chronic diseases in a list so we can create a bigger list with all of them produced
diseases <- c('hearte', 'hibpe', 'stroke', 'diabe', 'lunge', 'cancre', 'demene', 'asthmae')

@@

# Rename a few just for completeness
ageUK$Condition <- gsub("Cancer, recent", "Cancer", ageUK$Condition)
ageUK$Condition <- gsub("COPD", "Lung Disease (COPD)", ageUK$Condition)

@@

# REMOVE CONDITIONS FROM ageUK THAT ARE NOT IN FEM (may change in future)
#ageUK <- filter(ageUK, Condition != c('Asthma', 'Depression', 'Severe Mental Health Condition'))
ageUK <- filter(ageUK, Condition != 'Depression', Condition != 'Severe Mental Health Conditions')

@@

# Rename all the conditions to fit ageUK
# NOTE: Lung disease is not a perfect match, as ageUK only contains info on COPD
#       Therefore only validation from this will be that FEM is higher than ageUK
newFEM$Condition <- gsub("hearte", "Heart Problems", newFEM$Condition)
newFEM$Condition <- gsub("hibpe", "Hypertension", newFEM$Condition)
newFEM$Condition <- gsub("stroke", "Stroke", newFEM$Condition)
newFEM$Condition <- gsub("diabe", "Diabetes", newFEM$Condition)
newFEM$Condition <- gsub("lunge", "Lung Disease (COPD)", newFEM$Condition)
newFEM$Condition <- gsub("cancre", "Cancer", newFEM$Condition)
newFEM$Condition <- gsub("demene", "Dementia", newFEM$Condition)
newFEM$Condition <- gsub("asthmae", "Asthma", newFEM$Condition)

>>>>

# FEM 2014 summary
#FEM <- read_dta('ELSA_Baseline/ELSA_Baseline_summary.dta')
FEM <- read_dta('ELSA_AgeUK_core_valid/ELSA_AgeUK_core_valid_summary.dta')

@@

# Collect the age suffixes into a vector
keep_vars <- c(m_ages, f_ages)
# Now set up the chronic diseases in a list so we can create a bigger list with all of them produced
diseases <- c('hearte', 'hibpe', 'stroke', 'diabe', 'lunge', 'demene', 'asthmae')

@@

# Rename a few just for completeness
#ageUK$Condition <- gsub("Cancer, recent", "Cancer", ageUK$Condition)
ageUK$Condition <- gsub("COPD", "Lung Disease (COPD)", ageUK$Condition)

@@

# REMOVE CONDITIONS FROM ageUK THAT ARE NOT IN FEM (may change in future)
#ageUK <- filter(ageUK, Condition != c('Asthma', 'Depression', 'Severe Mental Health Condition'))
ageUK <- filter(ageUK, Condition != 'Depression', Condition != 'Severe Mental Health Conditions')
ageUK <- filter(ageUK, Condition != 'Cancer, recent')

@@

# Rename all the conditions to fit ageUK
# NOTE: Lung disease is not a perfect match, as ageUK only contains info on COPD
#       Therefore only validation from this will be that FEM is higher than ageUK
newFEM$Condition <- gsub("hearte", "Heart Problems", newFEM$Condition)
newFEM$Condition <- gsub("hibpe", "Hypertension", newFEM$Condition)
newFEM$Condition <- gsub("stroke", "Stroke", newFEM$Condition)
newFEM$Condition <- gsub("diabe", "Diabetes", newFEM$Condition)
newFEM$Condition <- gsub("lunge", "Lung Disease (COPD)", newFEM$Condition)
#newFEM$Condition <- gsub("cancre", "Cancer", newFEM$Condition)
newFEM$Condition <- gsub("demene", "Dementia", newFEM$Condition)
newFEM$Condition <- gsub("asthmae", "Asthma", newFEM$Condition)

### 2021-04-19 FEM_R/results.Rmd
Lots of small changes, committing altogether as would take forever to do piece by piece

This notebook will hold some initial testing and visualisation for the results section of the IJM paper.

```{r "setup", include=FALSE}
# Need to set up the environment
workingDir <- "/home/luke/Documents/E_FEM_clean/E_FEM/output/"
knitr::opts_knit$set(root.dir = workingDir)

require(tidyverse)
require(haven)
require(reshape2)
require(ggplot2)
#require(plyr)
#require(data.table)

@@

# Baselines
base <- read_dta('ELSA_core_base/ELSA_core_base_summary.dta')
cohort <- read_dta('ELSA_core_cohort/ELSA_core_cohort_summary.dta')

# Hearte (cohort and pop)
heart_c <- read_dta('ELSA_core_remove_hearte_c/ELSA_core_remove_hearte_c_summary.dta')
heart_p <- read_dta('ELSA_core_remove_hearte_p/ELSA_core_remove_hearte_p_summary.dta')

@@

Data has been read in, lets create some functions to visualise.

compareSurvivalCurve <- function(cohort, intervention, int_name,
                                 path='/home/luke/Documents/E_FEM_clean/Deliverables/E-FEM_Paper/figures/results/') {

@@

  ggsave(filename = paste0(int_name, '_survival_curve.png'),
         plot = p1,
         path = path)

  return(p1)

}

compareDeathAge <- function(base, int, int_name, path='/home/luke/Documents/E_FEM_clean/Deliverables/E-FEM_Paper/figures/results/') {

@@

  print(colnames(aDeath))

@@

  p1 <- ggplot(data = aDeath, aes(x = Year, y = Age, color = variable)) +
        geom_line() +
        labs(title = paste('Baseline vs', int_name), x = 'Year', y = 'Age at Death')

  ggsave(filename = paste0(int_name, '_death_age.png'),
         plot = p1,
         path = path)

  return(p1)
}
```

# Hearte

## Cohort

compareSurvivalCurve(coh, h, 'No Heart Disease')

cohortCDVis <- function(cohort, intervention, cds, path='/home/luke/Documents/E_FEM_clean/Deliverables/E-FEM_Paper/figures/results/') {

@@

  p1 <- ggplot(data = pivot.merged, aes(x = Age, y = value, color = source)) +
          geom_line() +
          facet_wrap(. ~ variable, scales = "free")

  ggsave(filename = 'noHearte_cd_lattice.png',
         plot = p1,
         path = path)

  return(p1)

}

cds <- c('p_hearte_all', 'p_cancre_all', 'p_stroke_all', 'p_diabe_all')

cohortCDVis(coh, h, cds)

## Population

compareDeathAge(b, h_p, 'No Heart Disease')

# Smoking

## Average Age at Death

b2 <- base
s <- smok

compareDeathAge(b2, smok, 'No Smoking')

## Chronic Diseases

baseCDVis <- function(base, int, cds, cds.rename, path='/home/luke/Documents/E_FEM_clean/Deliverables/E-FEM_Paper/figures/results/') {

  selBase <- base %>%
              select(c('year', all_of(cds)))
  colnames(selBase) <- c('Year', cds.rename)

  selInt <- int %>%
              select(c('year', all_of(cds)))
  colnames(selInt) <- c('Year', cds.rename)

@@

  ggsave(filename = 'noSmoke_cd_lattice.png',
         plot = p,
         path = path)

@@

cds <- c('p_lunge_all', 'p_hearte_all', 'p_cancre_all', 'p_stroke_all', 'p_diabe_all')
cds.rename <- c('Lung Disease', 'Heart', 'Cancer', 'Stroke', 'Diabetes')
baseCDVis(b2, s, cds, cds.rename)

visCDComparison <- function(base, int, int_name, cd, path='/home/luke/Documents/E_FEM_clean/Deliverables/E-FEM_Paper/figures/results/') {

  # For file naming and stuff
  if(cd == 'cancre') {
    dis <- 'Cancer'
  } else if(cd == 'diabe') {
    dis <- 'Diabetes'
  } else if(cd == 'hearte') {
    dis <- 'Heart Disease'
  } else if(cd == 'lunge') {
    dis <- 'Lung Disease'
  } else if(cd == 'stroke') {
    dis <- 'Stroke'
  }

@@

  selBase <- base %>%
              select(c('year', all_of(var))) %>%
              dplyr::rename('Baseline' = var)

  selInt <- int %>%
              select(c('year', all_of(var))) %>%
              dplyr::rename('Intervention' = var)

@@

  ggsave(filename = paste0(int_name, '_', dis, '_prev.png'),
         plot = p,
         path = path)

  return(p)

}

visCDComparison(b2, s, 'No Smoke', 'cancre')
visCDComparison(b2, s, 'No Smoke', 'diabe')
visCDComparison(b2, s, 'No Smoke', 'hearte')
visCDComparison(b2, s, 'No Smoke', 'lunge')
visCDComparison(b2, s, 'No Smoke', 'stroke')

# BMI

compareSurvivalCurveBMI <- function(cohort, int1, int2, int3,
                                 path='/home/luke/Documents/E_FEM_clean/Deliverables/E-FEM_Paper/figures/results/') {

@@

  ggsave(filename = 'BMI_survival_curves.png',
         plot = p1,
         path = path)

  return(p1)

}

@@

@@

# # Calculate age and survival curves
# c$Age <- (c$year - 2012) + 50
# bmi1$Age <- (bmi1$year - 2012) + 50
# bmi2$Age <- (bmi2$year - 2012) + 50
# bmi3$Age <- (bmi3$year - 2012) + 50
# c$Survival <- c$m_endpop_all / c$m_endpop_all[1]
# bmi1$Survival <- bmi1$m_endpop_all / bmi1$m_endpop_all[1]
# bmi2$Survival <- bmi2$m_endpop_all / bmi2$m_endpop_all[1]
# bmi3$Survival <- bmi3$m_endpop_all / bmi3$m_endpop_all[1]
# 
# cds <- c('p_hearte_all', 'p_cancre_all', 'p_stroke_all', 'p_diabe_all', 'a_bmi_all')
# 
# coh <- c %>%
#             select(Age, all_of(cds)) %>%
#             dplyr::rename(heart_cohort = p_hearte_all, cancer_cohort = p_cancre_all, 
#                           stroke_cohort = p_stroke_all, diabetes_cohort = p_diabe_all, 
#                           bmi_cohort = a_bmi_all)
# 
# b1 <- bmi1 %>%
#             select(Age, all_of(cds)) %>%
#             dplyr::rename(heart_bmi1 = p_hearte_all, cancer_bmi1 = p_cancre_all, 
#                           stroke_bmi1 = p_stroke_all, diabetes_bmi1 = p_diabe_all,
#                           bmi_bmi1 = a_bmi_all)
# 
# b2 <- bmi2 %>%
#             select(Age, all_of(cds)) %>%
#             dplyr::rename(heart_bmi2 = p_hearte_all, cancer_bmi2 = p_cancre_all, 
#                           stroke_bmi2 = p_stroke_all, diabetes_bmi2 = p_diabe_all,
#                           bmi_bmi2 = a_bmi_all)
# 
# b3 <- bmi3 %>%
#             select(Age, all_of(cds)) %>%
#             dplyr::rename(heart_bmi3 = p_hearte_all, cancer_bmi3 = p_cancre_all, 
#                           stroke_bmi3 = p_stroke_all, diabetes_bmi3 = p_diabe_all,
#                           bmi_bmi3 = a_bmi_all)
# 
# merged <- Reduce(merge, list(coh, b1, b2, b3))
# 
# pivot.merged <- pivot_longer(data = merged,
#                              cols = heart_cohort:bmi_bmi3,
#                              names_to = c('Feature', 'Scenario'),
#                              names_sep = '_',
#                              values_to = 'Value')
# 
# ggplot(data = filter(pivot.merged, Feature == 'bmi'), aes(x = Age, y = Value, color = Scenario)) +
#   geom_line()
# 
# ggplot(data = filter(pivot.merged, Feature == 'heart'), aes(x = Age, y = Value, color = Scenario)) +
#   geom_line()
# 
# ggplot(data = filter(pivot.merged, Feature == 'stroke'), aes(x = Age, y = Value, color = Scenario)) +
#   geom_line()
# 
# ggplot(data = filter(pivot.merged, Feature == 'diabetes'), aes(x = Age, y = Value, color = Scenario)) +
#   geom_line()

visCDComparisonBMI <- function(cohort, int1, int2, int3, cds, path='/home/luke/Documents/E_FEM_clean/Deliverables/E-FEM_Paper/figures/results/') {

  coh <- cohort %>%
              select(Age, all_of(cds)) %>%
              dplyr::rename(heart_cohort = p_hearte_all, cancer_cohort = p_cancre_all, 
                            stroke_cohort = p_stroke_all, diabetes_cohort = p_diabe_all, 
                            bmi_cohort = a_bmi_all)

  b1 <- int1 %>%
              select(Age, all_of(cds)) %>%
              dplyr::rename(heart_bmi1 = p_hearte_all, cancer_bmi1 = p_cancre_all, 
                            stroke_bmi1 = p_stroke_all, diabetes_bmi1 = p_diabe_all,
                            bmi_bmi1 = a_bmi_all)

  b2 <- int2 %>%
              select(Age, all_of(cds)) %>%
              dplyr::rename(heart_bmi2 = p_hearte_all, cancer_bmi2 = p_cancre_all, 
                            stroke_bmi2 = p_stroke_all, diabetes_bmi2 = p_diabe_all,
                            bmi_bmi2 = a_bmi_all)

  b3 <- int3 %>%
              select(Age, all_of(cds)) %>%
              dplyr::rename(heart_bmi3 = p_hearte_all, cancer_bmi3 = p_cancre_all, 
                            stroke_bmi3 = p_stroke_all, diabetes_bmi3 = p_diabe_all,
                            bmi_bmi3 = a_bmi_all)

  pivot.merged <- pivot_longer(data = merged,
                               cols = heart_cohort:bmi_bmi3,
                               names_to = c('Feature', 'Scenario'),
                               names_sep = '_',
                               values_to = 'Value')

  ggsave(filename = 'BMI_abmi.png',
         plot = p1,
         path = path)

  ggsave(filename = 'BMI_phearte.png',
         plot = p2,
         path = path)

  ggsave(filename = 'BMI_pstroke.png',
         plot = p3,
         path = path)

  ggsave(filename = 'BMI_pdiabe.png',
         plot = p4,
         path = path)

  return(list(p1, p2, p3, p4))
}

cds <- c('p_hearte_all', 'p_cancre_all', 'p_stroke_all', 'p_diabe_all', 'a_bmi_all')

@@

@@

@@

visCDComparison(c, bmi3, 'No Morbid', 'cancre')
visCDComparison(c, bmi3, 'No Morbid', 'diabe')
visCDComparison(c, bmi3, 'No Morbid', 'stroke')
visCDComparison(c, bmi3, 'No Morbid', 'hearte')
visCDComparison(c, bmi3, 'No Morbid', 'lunge')

@@

>>>>

# FEM Results

```{r "setup", include=FALSE}
# Need to set up the environment
workingDir <- "/home/luke/Documents/E_FEM_clean/tmp_output/"
knitr::opts_knit$set(root.dir = workingDir)

require(tidyverse)
require(haven)
require(reshape2)
require(ggplot2)
require(ggpubr)
#require(plyr)
#require(data.table)

@@

```{r}
## Read in all the data
# Baselines
base <- read_dta('ELSA_core_base/ELSA_core_base_summary.dta')
cohort <- read_dta('ELSA_core_cohort/ELSA_core_cohort_summary.dta')

# Hearte (cohort and pop)
#heart_c <- read_dta('ELSA_core_remove_hearte_c/ELSA_core_remove_hearte_c_summary.dta')
heart_p <- read_dta('ELSA_core_remove_hearte_p/ELSA_core_remove_hearte_p_summary.dta')

@@

# Drinking
nodrink <- read_dta('ELSA_core_remove_drink_p/ELSA_core_remove_drink_p_summary.dta')
noBadDrink <- read_dta('ELSA_core_remove_problem_drink_p/ELSA_core_remove_problem_drink_p_summary.dta')
```

## Functions

Define some functions here to run common visualisations.

```{r "functions", include=FALSE}

compareSurvivalCurve <- function(cohort, intervention, int_name, save=FALSE,
                                 path='/home/luke/Documents/E_FEM_clean/Deliverables/E-FEM_Paper/figures/results/') {

@@

  if(save) {
    ggsave(filename = paste0(int_name, '_survival_curve.png'),
         plot = p1,
         path = path)
  }

  return(p1)
}

compareDeathAge <- function(base, int, int_name, save=FALSE, path='/home/luke/Documents/E_FEM_clean/Deliverables/E-FEM_Paper/figures/results/') {

@@

@@

  p1 <- ggplot(data = aDeath, aes(x = Year, y = Age, color = variable)) +
        geom_smooth(lwd = 0.5) +
        labs(title = paste('Baseline vs', int_name), x = 'Year', y = 'Age at Death')

  if(save) {
    ggsave(filename = paste0(int_name, '_death_age.png'),
         plot = p1,
         path = path)
  }

  return(p1)
}

cohortCDVis <- function(cohort, intervention, cds, save=FALSE, path='/home/luke/Documents/E_FEM_clean/Deliverables/E-FEM_Paper/figures/results/') {

@@

  p1 <- ggplot(data = pivot.merged, aes(x = Age, y = value, color = source)) +
          geom_line() +
          facet_wrap(. ~ variable, scales = "free", ncol=2)

  if(save) {
    ggsave(filename = 'noHearte_cd_lattice.png',
         plot = p1,
         path = path)
  }

  return(p1)
}

baseCDVis <- function(base, intervention, int.name, cds, save=FALSE, path='/home/luke/Documents/E_FEM_clean/Deliverables/E-FEM_Paper/figures/results/') {

  baseMelt <- base %>%
              select(c('year', all_of(cds))) %>%
              melt(id.var='year', value.name = 'Prevalence_base')

  intMelt <- intervention %>%
              select(c('year', all_of(cds))) %>%
              melt(id.var='year', value.name = 'Prevalence_intervention')

  merged <- merge(baseMelt, intMelt)

  pivot.merged <- pivot_longer(data = merged,
                             cols = Prevalence_base:Prevalence_intervention,
                             names_to = c('Prevalence', 'source'),
                             names_sep = '_')
  pivot.merged <- select(pivot.merged, -Prevalence)

  p1 <- ggplot(data = pivot.merged, aes(x = year, y = value, color = source)) +
          geom_line() +
          facet_wrap(. ~ variable, scales = "free", ncol=2) +
          labs(title = int.name)

  return(p1)
}

baseCDVis2 <- function(base, int, cds, cds.rename, save=FALSE, path='/home/luke/Documents/E_FEM_clean/Deliverables/E-FEM_Paper/figures/results/') {

  selBase <- base %>%
              dplyr::select(c('year', all_of(cds)))
  colnames(selBase) <- c('Year', cds.rename)

  selInt <- int %>%
              dplyr::select(c('year', all_of(cds)))
  colnames(selInt) <- c('Year', cds.rename)

@@

  if(save) {
    ggsave(filename = 'noSmoke_cd_lattice.png',
         plot = p,
         path = path)
  }

@@

visCDComparison <- function(base, int, int_name, cd, save=FALSE, path='/home/luke/Documents/E_FEM_clean/Deliverables/E-FEM_Paper/figures/results/') {

  # For file naming and stuff
  if(cd == 'cancre') {
    dis <- 'Cancer'
  } else if(cd == 'diabe') {
    dis <- 'Diabetes'
  } else if(cd == 'hearte') {
    dis <- 'Heart Disease'
  } else if(cd == 'lunge') {
    dis <- 'Lung Disease'
  } else if(cd == 'stroke') {
    dis <- 'Stroke'
  } else if(cd == 'smoken') {
    dis <- 'Smoking'
  } else if(cd == 'employed') {
    dis <- 'Employed'
  } else if(cd == 'retired') {
    dis <- 'Retired'
  } else if(cd == 'anyadl') {
    dis <- 'ADLs'
  } else if(cd == 'anyiadl') {
    dis <- 'IADLs'
  }

@@

  selBase <- base %>%
              dplyr::select(c('year', all_of(var))) %>%
              dplyr::rename('Baseline' = var)

  selInt <- int %>%
              dplyr::select(c('year', all_of(var))) %>%
              dplyr::rename('Intervention' = var)

@@

  if(save) {
    ggsave(filename = paste0(int_name, '_', dis, '_prev.png'),
         plot = p,
         path = path)
  }

visCDComparisonCustom <- function(base, int, int_name, cd, save=FALSE, path='/home/luke/Documents/E_FEM_clean/Deliverables/E-FEM_Paper/figures/results/') {
  # For file naming and stuff
  if(cd == 'lunge') {
    tit <- 'Lung Disease'
    y.lab <- ' '
    prev <- TRUE
  } else if(cd == 'smoken') {
    tit <- 'Smoking'
    y.lab <- 'Prevalence'
    prev <- TRUE
  } else if(cd == 'age') {
    tit <- 'Average Age'
    y.lab <- 'Age'
    prev <- FALSE
  }

  if(prev) {
    var <- paste0('p_', cd, '_all')
  } else {
    var <- paste0('a_', cd, '_all')
  }

  selBase <- base %>%
              dplyr::select(c('year', all_of(var))) %>%
              dplyr::rename('Baseline' = var)
  selInt <- int %>%
              dplyr::select(c('year', all_of(var))) %>%
              dplyr::rename('Intervention' = var)
  melted <- merge(selBase, selInt, by = 'year') %>%
              reshape2::melt(id.var = 'year', value.name = 'Prevalence') %>%
              dplyr::rename('Scenario' = variable)

  p <- ggplot(data = melted, aes(x = year, y = Prevalence, color = Scenario)) +
          geom_line() +
          labs(title = tit, x = 'Year', y = y.lab)

compareSurvivalCurveBMI <- function(cohort, int1, int2, int3, save=FALSE,
                                 path='/home/luke/Documents/E_FEM_clean/Deliverables/E-FEM_Paper/figures/results/') {

@@

  if(save) {
    ggsave(filename = 'BMI_survival_curves.png',
         plot = p1,
         path = path)
  }

  return(p1)
}

visCDComparisonBMI <- function(cohort, int1, int2, int3, cds, save=FALSE, path='/home/luke/Documents/E_FEM_clean/Deliverables/E-FEM_Paper/figures/results/') {

  coh <- cohort %>%
              select(Age, all_of(cds)) %>%
              dplyr::rename(heart_cohort = p_hearte_all, cancer_cohort = p_cancre_all, 
                            stroke_cohort = p_stroke_all, diabetes_cohort = p_diabe_all, 
                            bmi_cohort = a_bmi_all, employed_cohort = p_employed_all,
                            retired_cohort = p_retired_all, adl_cohort = p_anyadl_all,
                            iadl_cohort = p_anyiadl_all)

  b1 <- int1 %>%
              select(Age, all_of(cds)) %>%
              dplyr::rename(heart_bmi1 = p_hearte_all, cancer_bmi1 = p_cancre_all, 
                            stroke_bmi1 = p_stroke_all, diabetes_bmi1 = p_diabe_all,
                            bmi_bmi1 = a_bmi_all, employed_bmi1 = p_employed_all,
                            retired_bmi1 = p_retired_all, adl_bmi1 = p_anyadl_all,
                            iadl_bmi1 = p_anyiadl_all)

  b2 <- int2 %>%
              select(Age, all_of(cds)) %>%
              dplyr::rename(heart_bmi2 = p_hearte_all, cancer_bmi2 = p_cancre_all, 
                            stroke_bmi2 = p_stroke_all, diabetes_bmi2 = p_diabe_all,
                            bmi_bmi2 = a_bmi_all, employed_bmi2 = p_employed_all,
                            retired_bmi2 = p_retired_all, adl_bmi2 = p_anyadl_all,
                            iadl_bmi2 = p_anyiadl_all)

  b3 <- int3 %>%
              select(Age, all_of(cds)) %>%
              dplyr::rename(heart_bmi3 = p_hearte_all, cancer_bmi3 = p_cancre_all, 
                            stroke_bmi3 = p_stroke_all, diabetes_bmi3 = p_diabe_all,
                            bmi_bmi3 = a_bmi_all, employed_bmi3 = p_employed_all,
                            retired_bmi3 = p_retired_all, adl_bmi3 = p_anyadl_all,
                            iadl_bmi3 = p_anyiadl_all)

  pivot.merged <- pivot_longer(data = merged,
                               cols = heart_cohort:iadl_bmi3,
                               names_to = c('Feature', 'Scenario'),
                               names_sep = '_',
                               values_to = 'Value')

  if(save) {
    ggsave(filename = 'BMI_abmi.png',
         plot = p1,
         path = path)
  }

  if(save) {
    ggsave(filename = 'BMI_phearte.png',
         plot = p2,
         path = path)
  }

  if(save) {
    ggsave(filename = 'BMI_pstroke.png',
         plot = p3,
         path = path)
  }

  if(save) {
    ggsave(filename = 'BMI_pdiabe.png',
         plot = p4,
         path = path)
  }

  p5 <- ggplot(data = filter(pivot.merged, Feature == 'employed'), aes(x = Age, y = Value, color = Scenario)) +
        geom_line() +
        labs(title = 'Employed', x = 'Age', y = 'Prevalence')

  p6 <- ggplot(data = filter(pivot.merged, Feature == 'retired'), aes(x = Age, y = Value, color = Scenario)) +
        geom_line() +
        labs(title = 'Retired', x = 'Age', y = 'Prevalence')

  p7 <- ggplot(data = filter(pivot.merged, Feature == 'adl'), aes(x = Age, y = Value, color = Scenario)) +
        geom_line() +
        labs(title = 'ADLs', x = 'Age', y = 'Prevalence')

  p8 <- ggplot(data = filter(pivot.merged, Feature == 'iadl'), aes(x = Age, y = Value, color = Scenario)) +
        geom_line() +
        labs(title = 'IADLs', x = 'Age', y = 'Prevalence')

  return(list(p1, p2, p3, p4, p5, p6, p7, p8))
}

@@

## Prevalence Change (2012-2050)

Here we will look at the % change in prevalence from 2012 - 2050, and compare these between variables.

Todo:
- Visualise results
  - Bar chart
  - Fancy table

```{r "prev_change"}

b <- base

b <- b %>%
        select(contains(c('year', 'cancre', 'diabe', 'hearte', 'lunge', 'stroke', 'demene', 'employed', 'anyadl', 'anyiadl', 'adl2', 'adl3p')))

b.2012 <- b %>% filter(year == 2012)
b.2050 <- b %>% filter(year == 2050)

cancre.change <- b.2050$p_cancre_all / b.2012$p_cancre_all
diabe.change <- b.2050$p_diabe_all / b.2012$p_diabe_all
hearte.change <- b.2050$p_hearte_all / b.2012$p_hearte_all
lunge.change <- b.2050$p_lunge_all / b.2012$p_lunge_all
stroke.change <- b.2050$p_stroke_all / b.2012$p_stroke_all
demene.change <- b.2050$p_demene_all / b.2012$p_demene_all
employed.change <- b.2050$p_employed_all / b.2012$p_employed_all
adl.change <- b.2050$p_anyadl_all / b.2012$p_anyadl_all
iadl.change <- b.2050$p_anyiadl_all / b.2012$p_anyiadl_all
adl2.change <- b.2050$p_adl2_all / b.2012$p_adl2_all
adl3p.change <- b.2050$p_adl3p_all / b.2012$p_adl3p_all

print(paste0('Cancer: ', cancre.change))
print(paste0('Diabetes: ', diabe.change))
print(paste0('Heart Disease: ', hearte.change))
print(paste0('Lung Disease: ', lunge.change))
print(paste0('Stroke: ', stroke.change))
print(paste0('Dementia: ', demene.change))
print(paste0('Employment: ', employed.change))
print(paste0('AnyADL: ', adl.change))
print(paste0('AnyIADL: ', iadl.change))
print(paste0('ADL2: ', adl2.change))
print(paste0('ADL3p: ', adl3p.change))

## Heart Disease Intervention (Population)

compareDeathAge(b, h_p, 'No Heart Disease', save=TRUE)

cds <- c('p_hearte_all', 'p_cancre_all', 'p_stroke_all', 'p_diabe_all', 'p_hibpe_all')
baseCDVis(b, h_p, 'No Heart Disease', cds)

econs <- c('p_employed_all', 'p_retired_all', 'p_anyadl_all', 'p_anyiadl_all', 'p_adl2_all', 'p_adl3p_all')
baseCDVis(b, h_p, 'No Heart Disease', econs)

## Smoking Intervention (Cohort)

c <- cohort
s <- smok

compareSurvivalCurve(c, smok, 'No Smoking')

cds <- c('p_lunge_all', 'p_hearte_all', 'p_cancre_all', 'p_smoken_all', 'p_stroke_all', 'p_diabe_all')
cds.rename <- c('Lung Disease', 'Heart', 'Cancer', 'Smoking', 'Stroke', 'Diabetes')
baseCDVis2(c, s, cds, cds.rename)

visCDComparison(c, s, 'No Smoke', 'cancre')
visCDComparison(c, s, 'No Smoke', 'diabe')
visCDComparison(c, s, 'No Smoke', 'hearte')
visCDComparison(c, s, 'No Smoke', 'lunge')
visCDComparison(c, s, 'No Smoke', 'stroke')
visCDComparison(c, s, 'No Smoke', 'smoken')
visCDComparison(c, s, 'No Smoke', 'employed')
visCDComparison(c, s, 'No Smoke', 'retired')
visCDComparison(c, s, 'No Smoke', 'anyadl')
visCDComparison(c, s, 'No Smoke', 'anyiadl')

smok.prev <- visCDComparisonCustom(c, s, 'No Smoke', 'smoken')
smok.lung <- visCDComparisonCustom(c, s, 'No Smoke', 'lunge')
#smok.age <- visCDComparisonCustom(b2, s, 'No Smoke', 'age')

ggarrange(smok.prev, smok.lung,
          labels = c('A', 'B', 'C'),
          common.legend = TRUE)
```

# Lets get the results by age group, sex and education level
# For this we need detailed output
#c_det <- read_dta('ELSA_core_cohort')
#s <- smok

cohortVisByGroup <- function(cohort, intervention, cds, groups, save=FALSE) {

  cohMelt <- cohort %>%
              select(c('Age', all_of(cds), all_of(groups))) %>%
              melt(id.var=c('Age', 'male', 'educ'), value.name = 'Prevalence_cohort')

  intMelt <- intervention %>%
              select(c('Age', all_of(cds), all_of(groups))) %>%
              melt(id.var=c('Age', 'male', 'educ'), value.name = 'Prevalence_intervention')

  return(pivot.merged)
}

#cds <- c('p_lunge_all', 'p_hearte_all', 'p_cancre_all', 'p_smoken_all', 'p_stroke_all', 'p_diabe_all')
#groups <- c('male', 'age', 'educ')

#output <- cohortVisByGroup(c, s, cds, groups)

## BMI Reduction Interventions

@@

cds <- c('p_hearte_all', 'p_cancre_all', 'p_stroke_all', 'p_diabe_all', 'a_bmi_all', 
         'p_employed_all', 'p_retired_all', 'p_anyadl_all', 'p_anyiadl_all')

@@

visCDComparison(c, bmi3, 'No Morbid', 'cancre')
visCDComparison(c, bmi3, 'No Morbid', 'diabe')
visCDComparison(c, bmi3, 'No Morbid', 'stroke')
visCDComparison(c, bmi3, 'No Morbid', 'hearte')
visCDComparison(c, bmi3, 'No Morbid', 'lunge')
visCDComparison(c, bmi3, 'No Morbid', 'employed')
visCDComparison(c, bmi3, 'No Morbid', 'retired')
visCDComparison(c, bmi3, 'No Morbid', 'anyadl')
visCDComparison(c, bmi3, 'No Morbid', 'anyiadl')

@@

## Quit Alcohol Intervention (Just out of interest)

@@

b3 <- base
nod <- nodrink
nopd <- noBadDrink

compareDeathAge(b3, nod, "No Drink")
compareDeathAge(b3, nopd, "No Problem Drink")

cds <- c('p_hearte_all', 'p_cancre_all', 'p_stroke_all', 'p_diabe_all')
baseCDVis(b3, nod, 'No Drink', cds)

econs <- c('p_employed_all', 'p_retired_all', 'p_anyadl_all', 'p_anyiadl_all')
baseCDVis(b3, nod, 'No Drink', econs)

baseCDVis(b3, nopd, 'No Problem Drink', cds)
baseCDVis(b3, nopd, 'No Problem Drink', econs)

@@

# OLD DEFUNKT CODE

### Hearte Cohort Intervention
```{r}

# Survival Curves
compareSurvivalCurve(coh, h, 'No Heart Disease')

# Chronic Diseases
cds <- c('p_hearte_all', 'p_cancre_all', 'p_stroke_all', 'p_diabe_all')
cohortCDVis(coh, h, cds)

# Economic Factors
econs <- c('p_employed_all', 'p_retired_all', 'p_anyadl_all', 'p_anyiadl_all')
cohortCDVis(coh, h, econs)
